The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl

### 2018-01-24 introduction.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper

X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes charge and energy transfer \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003} are possible.

@@

>>>>

X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions (Ref.\ \citep{smith17:13909} and references therein), and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decays. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as charge and energy transfer \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708,ceolin17:263003} are possible.

@@

%refs clusters??:
%A. Lindblad, R. F. Fink, H. Bergersen, M. Lundwall, T. Rander, R. Feifel, G. Öhrwall, M. Tchaplyguine, U.Hergenhahn, S. Svensson, O. Björneholm, The Journal of Chemical %Physics 123, 211101 (2005)
%M. Tchaplyguine, A. Kivimäki, S. Peredkov, S. L. Sorensen, G. Öhrwall, J. Schulz, M. Lundwall, T. Rander, A. Lindblad, A. Rosso, S. Svensson, N. Mårtensson, O. %Björneholm, The Journal of Chemical Physics, 127, 124314 (2007)

### 2018-01-24 methods.tex
jan 24 (denis' corrections & tsveta's)
Shift explained as resulting from internal ionization, an argument for
the attribution of island C as 2p-2 3d state based on the CT paper

\section{Methods} \label{sec:methods}
\subsection{Experimental}
% Denis, please have a look at the experimental part and see if all the references have been correctly included
For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}. A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes manipulator in front of the spectrometer lens. Two holes of 2\,mm diameter allow the photons to go in and out of the tube. At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer. The microjet head is mostly composed of a 30\,$\mu$m diameter vertical glass capillary facing a temperature-controlled catcher in CuBe having a 300\,$\mu$m hole, and a camera. Piezo motors allow their precise alignment relative to each other and to the photon beam. The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid. For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a HPLC pump with a constant flux of 1.6\,ml/min. The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio. The pressure in the main chamber is kept below the 10$^{−5}$\,mbar range whereas it is kept at about 10$^{−4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON. Our equipment is an updated version of the equipment used in the reference \cite{faubel88:269}. The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water. Filtering and degazing procedures were systematically performed before injecting the solution. The spectrometer resolution of about 0.6 eV was achieved with the 500 eV pass energy and 0.5\,mm slits. The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively

>>>>

\section{Methods} \label{sec:methods}
\subsection{Experimental}
% Denis, please have a look at the experimental part and see if all the references have been correctly included
For the present experiment we used the newly operational microjet setup that was specifically designed for the HAXPES station of the GALAXIES beamline \citep{ceolin13:188,rueff15:175}. A differentially-pumped tube in which the microjet head is inserted, is mounted on a 3-axes manipulator in front of the spectrometer lens. Two holes of 2\,mm diameter allow the photons to go in and out. At the end of the tube and in front of the lens, a 500\,$\mu$m diameter hole skimmer allows the electrons created at the interaction point to go in the direction of the spectrometer. The microjet head is mostly composed of a 30\,$\mu$m diameter vertical glass capillary facing a temperature-controlled catcher in CuBe having a 300\,$\mu$m hole, and a camera. Piezo motors allow their precise alignment relative to each other and to the photon beam. The catcher is placed at a distance of about 5\,mm from the capillary and is permanently pumped in order to extract the liquid. For the present experiment, a 0.5M KCl aqueous solution is injected in the capillary by a HPLC pump with a constant flux of 1.6\,ml/min. The alignment of the setup is performed on a salted aqueous solution by measuring the O1s XPS peak intensity and by optimizing the liquid phase vs gas phase ratio. The pressure in the main chamber is kept below the 10$^{-5}$\,mbar range whereas it is kept at about 10$^{-4}$\,mbar in the differentially-pumped tube when the HPLC pump is ON. Our equipment is an updated version of the equipment used in the reference \cite{faubel88:269}. The aqueous potassium chloride solution was prepared by mixing >99\% KCl salt with deionized water. Filtering and degazing procedures were systematically performed before injecting the solution. The spectrometer resolution of about 0.6 eV was achieved with the 500 eV pass energy and 0.5\,mm slits. The photon energy resolution achieved at 2.8\,keV and 3.6\,keV was about 0.3\,eV and 0.4\,eV, respectively
